pairwise plot of flash result of flash Z-score

### 2017-05-03 analysis/pairwiseplotofflashgtexzscore.Rmd
Files commited by wflow_commit.

@@

>>>>

### plot of $l_1$ vs $l_3$

@@

### plot $f_1$ vs $f_3$

```{r}
i = 1
j = 3
plot(b_flash$f[,i],b_flash$f[,j],col = "grey",pch = 16)

```

## logcpm of count

here I use
- 2 brain tissues
- testis + pituitary
- 2 skin
- Mammary+ adipose
- 2 heart
- uterus + Ovary

for each tissue, we random pick 50 smaples.

```{r}
bfl = readRDS("../data/GTExdata/logcpm/sixpairssubsample/bflash_varcol.rds")
```

I run flash with K=60 and it provide 60 factors in greedy algorithm, which mean it didn't stop. I run backfitting procedure with 6 iteration due to the time limit, it still provide 60 factors.

I am not sure the factor are useful a

```{r}
color_six = c(rep("#eeee00",100),rep("#aaaaaa",50),rep("#aaff99",50),
              rep("#0000ff",50),rep("#7777ff",50),
              rep("#ffaa00",50),rep("#33cccc",50),
              rep("#9900ff",50),rep("#660099",50),
              rep("#ff66ff",50),rep("#ffaaff",50))

par(mfrow = c(3,3),mar = c(5,4,4,2)-1.8)
for(i in 1:60){
  barplot(bfl$l[,i],col = color_six,border = color_six)
}
```
